---
title: "L1 -- Introduction to _Bioconductor_"
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
vignette: >
  % \VignetteIndexEntry{L1 -- Introduction to Bioconductor}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE}
suppressPackageStartupMessages({
    library(GenomicRanges)
    library(SummarizedExperiment)
})
```

Author: Martin Morgan
  (<a href="mailto:mtmorgan@fhcrc.org">mtmorgan@fhcrc.org</a>)<br />
Date: 26-28 October, 2015<br />

- Familiarity with _R_. The diversity of analysis challenges addressed
  by _Bioconductor_. The role of _Bioconductor_ packages in specific
  work flow steps. _Bioconductor_ resources for help and effective
  use. Primary packages: [GenomicRanges][], [SummarizedExperiment][].

# Interactivity / lecture: Sequence analysis work flows

# _R_ 

- vectors, classes, and methods
- help!

## Lab exercise: common data transformations

# _Bioconductor_

## Presentation: project tour

- [biocViews][]
    - Types of _Bioconductor_ packages: software, annotation, experiment data
- Landing pages
- Support, course material, and other resources

## Interactivity / lecture: example _Bioconductor_ packages

- [Biostrings][] and phiX174
- [GenomicRanges][]
- [SummarizedExperiment][]

[biocViews]: https://bioconductor.org/packages/
[Biostrings]: https://bioconductor.org/packages/Biostrings
[GenomicRanges]: https://bioconductor.org/packages/GenomicRanges
[SummarizedExperiment]: https://bioconductor.org/packages/SummarizedExperiment